Enhancement of SDR in Thessaloniki

### 2024-09-03 GHI_enh_read_aod_brewer.tex
Commit 2024-09-03 09:09

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-02}

@@

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}@{}}
\caption{AOD change \%/y}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.2558 & AOD\_292 \\
0.0385 & AOD\_292.5 \\
0.04534 & AOD\_293 \\
0.06775 & AOD\_293.5 \\
0.05734 & AOD\_294 \\
0.0763 & AOD\_294.5 \\
0.0831 & AOD\_295 \\
0.08266 & AOD\_295.5 \\
0.1019 & AOD\_296 \\
0.09853 & AOD\_296.5 \\
0.09384 & AOD\_297 \\
0.08095 & AOD\_297.5 \\
0.09393 & AOD\_298 \\
0.08817 & AOD\_298.5 \\
0.0804 & AOD\_299 \\
0.07093 & AOD\_299.5 \\
0.06308 & AOD\_300 \\
0.05071 & AOD\_300.5 \\
0.05359 & AOD\_301 \\
0.04396 & AOD\_301.5 \\
0.03347 & AOD\_302 \\
0.02571 & AOD\_302.5 \\
0.02131 & AOD\_303 \\
0.01803 & AOD\_303.5 \\
0.01171 & AOD\_304 \\
0.01022 & AOD\_304.5 \\
0.005416 & AOD\_305 \\
0.0005074 & AOD\_305.5 \\
0.002836 & AOD\_306 \\
0.0001914 & AOD\_306.5 \\
0.001028 & AOD\_307 \\
0.0002915 & AOD\_307.5 \\
0.01176 & AOD\_308 \\
0.02345 & AOD\_308.5 \\
0.02512 & AOD\_309 \\
0.02872 & AOD\_309.5 \\
0.03807 & AOD\_310 \\
0.04033 & AOD\_310.5 \\
0.04404 & AOD\_311 \\
0.04732 & AOD\_311.5 \\
0.04988 & AOD\_312 \\
0.05461 & AOD\_312.5 \\
0.05661 & AOD\_313 \\
0.06141 & AOD\_313.5 \\
0.05901 & AOD\_314 \\
0.05361 & AOD\_314.5 \\
0.0447 & AOD\_315 \\
0.03122 & AOD\_315.5 \\
0.02879 & AOD\_316 \\
0.02784 & AOD\_316.5 \\
0.02667 & AOD\_317 \\
0.02556 & AOD\_317.5 \\
0.02617 & AOD\_318 \\
0.02414 & AOD\_318.5 \\
0.01576 & AOD\_319 \\
0.007456 & AOD\_319.5 \\
0.002617 & AOD\_320 \\
0.00727 & AOD\_320.5 \\
0.0097 & AOD\_321 \\
0.01868 & AOD\_321.5 \\
0.02508 & AOD\_322 \\
0.02554 & AOD\_322.5 \\
0.02652 & AOD\_323 \\
0.02711 & AOD\_323.5 \\
0.03271 & AOD\_324 \\
0.03674 & AOD\_324.5 \\
0.03564 & AOD\_325 \\
0.04207 & AOD\_325.5 \\
0.04356 & AOD\_326 \\
0.04334 & AOD\_326.5 \\
0.04177 & AOD\_327 \\
0.04679 & AOD\_327.5 \\
0.04267 & AOD\_328 \\
0.03719 & AOD\_328.5 \\
0.03491 & AOD\_329 \\
0.03328 & AOD\_329.5 \\
0.03067 & AOD\_330 \\
0.03602 & AOD\_330.5 \\
0.03564 & AOD\_331 \\
0.03208 & AOD\_331.5 \\
0.02064 & AOD\_332 \\
0.01897 & AOD\_332.5 \\
0.02294 & AOD\_333 \\
0.02197 & AOD\_333.5 \\
0.02225 & AOD\_334 \\
0.02282 & AOD\_334.5 \\
0.02284 & AOD\_335 \\
0.02381 & AOD\_335.5 \\
0.02606 & AOD\_336 \\
0.02517 & AOD\_336.5 \\
0.02722 & AOD\_337 \\
0.02877 & AOD\_337.5 \\
0.03161 & AOD\_338 \\
0.03294 & AOD\_338.5 \\
0.03393 & AOD\_339 \\
0.03063 & AOD\_339.5 \\
0.02624 & AOD\_340 \\
0.02005 & AOD\_340.5 \\
0.02407 & AOD\_341 \\
0.02232 & AOD\_341.5 \\
0.02444 & AOD\_342 \\
0.02502 & AOD\_342.5 \\
0.02645 & AOD\_343 \\
0.0247 & AOD\_343.5 \\
0.02531 & AOD\_344 \\
0.02526 & AOD\_344.5 \\
0.02374 & AOD\_345 \\
0.02159 & AOD\_345.5 \\
0.02034 & AOD\_346 \\
0.02048 & AOD\_346.5 \\
0.01923 & AOD\_347 \\
0.01956 & AOD\_347.5 \\
0.0214 & AOD\_348 \\
0.01945 & AOD\_348.5 \\
0.01227 & AOD\_349 \\
0.01165 & AOD\_349.5 \\
0.01124 & AOD\_350 \\
0.009548 & AOD\_350.5 \\
0.008288 & AOD\_351 \\
0.006796 & AOD\_351.5 \\
0.004561 & AOD\_352 \\
0.004843 & AOD\_352.5 \\
0.003653 & AOD\_353 \\
0.0007953 & AOD\_353.5 \\
0.001056 & AOD\_354 \\
0.004497 & AOD\_354.5 \\
0.003201 & AOD\_355 \\
0.009072 & AOD\_355.5 \\
0.00913 & AOD\_356 \\
0.00913 & AOD\_356.5 \\
0.009986 & AOD\_357 \\
0.01327 & AOD\_357.5 \\
0.01149 & AOD\_358 \\
0.008446 & AOD\_358.5 \\
0.004012 & AOD\_359 \\
0.00145 & AOD\_359.5 \\
0.001221 & AOD\_360 \\
0.00208 & AOD\_360.5 \\
0.003965 & AOD\_361 \\
0.01953 & AOD\_361.5 \\
0.06372 & AOD\_362 \\
0.066 & AOD\_362.5 \\
0.05968 & AOD\_363 \\
\end{longtable}

\begin{verbatim}
range 0.0001914191 0.2557606 
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-09-03}

@@

\begin{verbatim}
Drop data with clouds
\end{verbatim}

@@

\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.1806}}@{}}
\caption{AOD change \%/y}\tabularnewline
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\centering
slope\_pCpY
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
AOD
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
0.07593 & AOD\_292 \\
0.1666 & AOD\_292.5 \\
0.09945 & AOD\_293 \\
0.09468 & AOD\_293.5 \\
0.05937 & AOD\_294 \\
0.06021 & AOD\_294.5 \\
0.07722 & AOD\_295 \\
0.08395 & AOD\_295.5 \\
0.09015 & AOD\_296 \\
0.0975 & AOD\_296.5 \\
0.09944 & AOD\_297 \\
0.08816 & AOD\_297.5 \\
0.09295 & AOD\_298 \\
0.09489 & AOD\_298.5 \\
0.09257 & AOD\_299 \\
0.09279 & AOD\_299.5 \\
0.09115 & AOD\_300 \\
0.09293 & AOD\_300.5 \\
0.09517 & AOD\_301 \\
0.1004 & AOD\_301.5 \\
0.1001 & AOD\_302 \\
0.09831 & AOD\_302.5 \\
0.1008 & AOD\_303 \\
0.1019 & AOD\_303.5 \\
0.1023 & AOD\_304 \\
0.1034 & AOD\_304.5 \\
0.102 & AOD\_305 \\
0.1014 & AOD\_305.5 \\
0.1026 & AOD\_306 \\
0.09934 & AOD\_306.5 \\
0.09853 & AOD\_307 \\
0.1004 & AOD\_307.5 \\
0.1002 & AOD\_308 \\
0.1001 & AOD\_308.5 \\
0.1017 & AOD\_309 \\
0.1028 & AOD\_309.5 \\
0.1056 & AOD\_310 \\
0.1059 & AOD\_310.5 \\
0.1063 & AOD\_311 \\
0.1058 & AOD\_311.5 \\
0.1036 & AOD\_312 \\
0.1066 & AOD\_312.5 \\
0.1056 & AOD\_313 \\
0.1056 & AOD\_313.5 \\
0.1067 & AOD\_314 \\
0.1065 & AOD\_314.5 \\
0.1072 & AOD\_315 \\
0.108 & AOD\_315.5 \\
0.1068 & AOD\_316 \\
0.1073 & AOD\_316.5 \\
0.1079 & AOD\_317 \\
0.108 & AOD\_317.5 \\
0.1068 & AOD\_318 \\
0.1052 & AOD\_318.5 \\
0.1059 & AOD\_319 \\
0.1054 & AOD\_319.5 \\
0.106 & AOD\_320 \\
0.1062 & AOD\_320.5 \\
0.1071 & AOD\_321 \\
0.1034 & AOD\_321.5 \\
0.1031 & AOD\_322 \\
0.1036 & AOD\_322.5 \\
0.104 & AOD\_323 \\
0.1036 & AOD\_323.5 \\
0.1044 & AOD\_324 \\
0.104 & AOD\_324.5 \\
0.1036 & AOD\_325 \\
0.1024 & AOD\_325.5 \\
0.1032 & AOD\_326 \\
0.1016 & AOD\_326.5 \\
0.1008 & AOD\_327 \\
0.1025 & AOD\_327.5 \\
0.1036 & AOD\_328 \\
0.1041 & AOD\_328.5 \\
0.1047 & AOD\_329 \\
0.1042 & AOD\_329.5 \\
0.1059 & AOD\_330 \\
0.1055 & AOD\_330.5 \\
0.1041 & AOD\_331 \\
0.1045 & AOD\_331.5 \\
0.1038 & AOD\_332 \\
0.1074 & AOD\_332.5 \\
0.1079 & AOD\_333 \\
0.1083 & AOD\_333.5 \\
0.1089 & AOD\_334 \\
0.1102 & AOD\_334.5 \\
0.1103 & AOD\_335 \\
0.1098 & AOD\_335.5 \\
0.11 & AOD\_336 \\
0.1103 & AOD\_336.5 \\
0.11 & AOD\_337 \\
0.1108 & AOD\_337.5 \\
0.1092 & AOD\_338 \\
0.1103 & AOD\_338.5 \\
0.1097 & AOD\_339 \\
0.109 & AOD\_339.5 \\
0.1087 & AOD\_340 \\
0.1091 & AOD\_340.5 \\
0.1094 & AOD\_341 \\
0.1097 & AOD\_341.5 \\
0.1098 & AOD\_342 \\
0.1114 & AOD\_342.5 \\
0.1088 & AOD\_343 \\
0.1086 & AOD\_343.5 \\
0.1088 & AOD\_344 \\
0.1082 & AOD\_344.5 \\
0.1083 & AOD\_345 \\
0.1104 & AOD\_345.5 \\
0.1104 & AOD\_346 \\
0.1103 & AOD\_346.5 \\
0.1091 & AOD\_347 \\
0.109 & AOD\_347.5 \\
0.1085 & AOD\_348 \\
0.1082 & AOD\_348.5 \\
0.1093 & AOD\_349 \\
0.1079 & AOD\_349.5 \\
0.1062 & AOD\_350 \\
0.1042 & AOD\_350.5 \\
0.1049 & AOD\_351 \\
0.104 & AOD\_351.5 \\
0.1034 & AOD\_352 \\
0.1042 & AOD\_352.5 \\
0.1075 & AOD\_353 \\
0.1079 & AOD\_353.5 \\
0.1085 & AOD\_354 \\
0.1135 & AOD\_354.5 \\
0.1145 & AOD\_355 \\
0.1137 & AOD\_355.5 \\
0.1135 & AOD\_356 \\
0.1151 & AOD\_356.5 \\
0.1154 & AOD\_357 \\
0.1148 & AOD\_357.5 \\
0.1163 & AOD\_358 \\
0.1174 & AOD\_358.5 \\
0.1179 & AOD\_359 \\
0.1181 & AOD\_359.5 \\
0.1197 & AOD\_360 \\
0.1188 & AOD\_360.5 \\
0.1179 & AOD\_361 \\
0.1155 & AOD\_361.5 \\
0.1236 & AOD\_362 \\
0.1082 & AOD\_362.5 \\
0.08471 & AOD\_363 \\
\end{longtable}

\begin{verbatim}
range 0.0593665 0.1665588 
\end{verbatim}
